### 2013-12-17 poster/poster.tex
format poster

\usepackage{times} % Use the times font
%\usepackage{palatino} % Uncomment to use the Palatino font

@@

\color{DarkSlateGray} % DarkSlateGray color for the rest of the content

\section*{Problem}

\begin{tabular} {l | l}
    \textbf{Single Controller Architecture} & \textbf{Distributed controller Architecture} \\
    \hline
    Responsiveness & Communication overhead \\
       Scalability & Scalability of global network view \\
       Reliability & Network state inconsistencies \\
                   & Management barriers across networks
\end{tabular}

\textbf{Trade-offs}
\begin{itemize}
    \item Consistency vs. Responsiveness
    \item Optimality vs. I dont know what
    \item Application design complexity (Architecture aware vs. agnostic)
\end{itemize}

\textbf{Our Goals}
\begin{itemize}
    \item Make control applications agnostic to architecture
    \item Reduce communication overhead
    \item Minimize network state inconsistencies
    \item Enable smooth transition across management barriers
    \item Handle changes locally
\end{itemize}

@@

\section*{Our solution}
\begin{itemize}
    \item Hierarchical arrangement of controllers
    \item One switch abstraction
    \item Translate messages across hierarchical layers
\end{itemize}

@@

%Gourav - I'm starting from here ownwards: 
%----------------------------------------------------------------------------------------
%	RESULTS 
%----------------------------------------------------------------------------------------

\section*{Experimental set up}

\begin{itemize}
%\item We simulated a dummy control application on both hierarchical and flat controller architectures, with same network topology and flow arrival distribution.
\item Flow data (6000 MapReduce jobs) was generated by sampling historical Hadoop traces on a 600 machine cluster at Facebook (1 million jobs). A dummy MapReduce application choses directory, map and reduce nodes randomly for each job.
\item Topology: 600 hosts connected through a network of 200 switches and 10 Gbps links. The cluster is divided into 10 equally-sized control domains.
\item TE-cum-routing coutrol application: When a new flow arrives, it finds the path with minimum maximum utilization. If multiple such paths exist (which is frequently the case, due to a large network), shortest path (in term of number of hops) is chosen.
\end{itemize}

\section*{Metrices}
\begin{itemize}
\item Path length (number of hops) of the routes assigned to flows.
\item Maximum link utilization of the path assigned to flows.
\item Communication overhead (number of messages exchanged between controllers) for seting up routes for flows.   
\end{itemize}

@@

\section*{Results}
Hierarchical architecture reduces communication overhead (Figure \ref{fig:msg}) by an order of magnitude while comprimising modestly on optimality: shortest path length (17.4\%) (Figure \ref{fig:path}) and minimum maximum link utilization (12.8\%) (Figure \ref{fig:util}).

@@

%\color{SaddleBrown} % SaddleBrown color for the conclusions to make them stand out

%\section*{Conclusions}

@@

@@

\subsection*{Source code}
https://github.com/MugiwaraLuffy/ACN/

>>>>

\usepackage{times} % Use the times font
\usepackage{palatino} % Uncomment to use the Palatino font

@@

\color{SaddleBrown}% DarkSlateGray color for the rest of the content
\section*{PROBLEM}
\color{DarkSlateGray}
\begin{tabular} {l | l}
    \textbf{Single Controller Architecture} & \textbf{Distributed controller Architecture} \\
    \hline
    Responsiveness & Communication overhead \\
       Scalability & Scalability of global network view \\
       Reliability & Network state inconsistencies \\
                   & Management barriers across networks
\end{tabular}

\textbf{Trade-offs}
\begin{itemize}
    \item Consistency vs. Responsiveness
    \item Optimality vs. I dont know what
    \item Application design complexity (Architecture aware vs. agnostic)\\
\end{itemize}

\textbf{Goals}
\begin{itemize}
    \item Make control applications agnostic to architecture
    \item Reduce communication overhead
    \item Minimize network state inconsistencies
    \item Enable smooth transition across management barriers
    \item Handle changes locally \\
\end{itemize}

@@

\color{SaddleBrown}
\section*{PROPOSED SOLUTION}
\color{DarkSlateGray}
\begin{itemize}
    \item Hierarchical arrangement of controllers
    \item One switch abstraction
    \item Translate messages across hierarchical layers
\end{itemize}

@@

%Gourav - I'm starting from here ownwards: 
%----------------------------------------------------------------------------------------
%	RESULTS 
%----------------------------------------------------------------------------------------
\color{SaddleBrown}
\section*{EXPERIMENTAL SETUP}
\color{DarkSlateGray}
\begin{itemize}
%\item We simulated a dummy control application on both hierarchical and flat controller architectures, with same network topology and flow arrival distribution.
\item Flow data (6000 MapReduce jobs) was generated by sampling historical Hadoop traces on a 600 machine cluster at Facebook (1 million jobs). A dummy MapReduce application choses directory, map and reduce nodes randomly for each job.
\item Topology: 600 hosts connected through a network of 200 switches and 10 Gbps links. The cluster is divided into 10 equally-sized control domains.
\item TE-cum-routing coutrol application: When a new flow arrives, it finds the path with minimum maximum utilization. If multiple such paths exist (which is frequently the case, due to a large network), shortest path (in term of number of hops) is chosen.
\end{itemize}

\color{SaddleBrown}
\section*{METRICS}
\color{DarkSlateGray}
\begin{itemize}
\item Path length (number of hops) of the routes assigned to flows.
\item Maximum link utilization of the path assigned to flows.
\item Communication overhead (number of messages exchanged between controllers) for seting up routes for flows.   
\end{itemize}

@@

\color{SaddleBrown}
\section*{RESULTS}
\color{DarkSlateGray}
Hierarchical architecture reduces communication overhead (Figure \ref{fig:msg}) by an order of magnitude while comprimising modestly on optimality: shortest path length (17.4\%) (Figure \ref{fig:path}) and minimum maximum link utilization (12.8\%) (Figure \ref{fig:util}).

@@

\color{SaddleBrown} % SaddleBrown color for the conclusions to make them stand out

%\section*{CONCLUSION}

@@

\color{SaddleBrown}
\subsection*{SOURCE CODE}
\color{DarkSlateGray}
https://github.com/MugiwaraLuffy/ACN/

@@
